### 2010-12-07 report/report.tex
fixed a few things
explore plots in

\edit{proofread}

@@

We have done complete runs of 3 different initial parameter vectors
for random search, uniform random hill climbing, Gaussian random hill
climbing, policy gradient descent, Nelder-Mead simplex, and linear
regression.  We also evaluated the SVM regression and HyperNEAT
methods, but these methods were more experimental, and thus we do not
yet have the same volume of data for these runs.  We developed several
gaits that were about 4 times faster than the original hand-coded
gait.

\edit{Convert to Table}

\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & A       & B      & C      &  Average \\
\hline                                                               
\hline                                                               
Previous hand-coded gait                 & --      & --     & --     &  5.16 \\
\hline                                                                 
Random search                            & 6.04    & 17.26  & 4.90   &  9.40 \\
\hline                                                                 
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   &  7.83 \\
\hline                                                                 
Gaussian Random Hill Climbing            & 3.10    & 13.59  & 13.40  &  10.03 \\
\hline                                                                 
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   &  6.32 \\
\hline                                                                 
Nelder-Mead simplex                      & 8.51    & 13.62  & 14.83  &  12.32 \\
\hline                                                                 
Linear Regression                        & 27.58   & 12.51  & 1.95   &  14.01 \\
%\hline                                                                
%SVM Regression                           & ???     & ???    & ???   &   \\
%\hline                                                                
%Evolutionary Neural Network (HyperNEAT)  & ???     & ???    & ???   &   \\
\hline
\end{tabular}

\edit{Caption: The best gaits found for each starting vector and
  algorithm, in body lengths per minute.}

@@

In addition to running strategies to optimize parameterized gaits, we
also ......

We also coded \code{explore\_dimensions} to collect data for dimension
varying plots. We intend to do further explore this by running
\code{explore\_dimension} around a parameter that produces a medium-good gait.

\edit{Jason: add exploration runs}

>>>>

@@

We have done complete runs of 3 different initial parameter vectors
for random search, uniform random hill climbing, Gaussian random hill
climbing, policy gradient descent, Nelder-Mead simplex, and linear
regression.  We also evaluated the SVM regression and HyperNEAT
methods, but these methods were more experimental, and thus we do not
yet have the same volume of data for these runs.  We developed several
gaits that were about 4 times faster than the original hand-coded
gait.  Results are shown in \tabref{results_table}.

\begin{table}
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & A       & B      & C      &  Average \\
\hline                                                               
\hline                                                               
Previous hand-coded gait                 & --      & --     & --     &  5.16 \\
\hline                                                                 
Random search                            & 6.04    & 17.26  & 4.90   &  9.40 \\
\hline                                                                 
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   &  7.83 \\
\hline                                                                 
Gaussian Random Hill Climbing            & 3.10    & 13.59  & 13.40  &  10.03 \\
\hline                                                                 
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   &  6.32 \\
\hline                                                                 
Nelder-Mead simplex                      & 8.51    & 13.62  & 14.83  &  12.32 \\
\hline                                                                 
Linear Regression                        & 27.58   & 12.51  & 1.95   &  14.01 \\
%\hline                                                                
%SVM Regression                           & ???     & ???    & ???   &   \\
%\hline                                                                
%Evolutionary Neural Network (HyperNEAT)  & ???     & ???    & ???   &   \\
\hline
\end{tabular}
\caption{The best gaits found for each starting vector and algorithm,
  in body lengths per minute.}
\tablabel{results_table}
\end{center}
\end{table}

@@

In addition to running strategies to optimize parameterized gaits, we
also wanted to investigate the space of possible gaits.  To accomplish
this, we selected a parameter vector that resulted in motion, but not
an exceptional gait, and plotted performance along each dimension
individually.  In addition, we duplicated each measurement to be able
to estimate the measurement noise at each point.  Results for this
exploration are shown in \figref{explore_dim_1} through
\figref{explore_dim_5}.

\figvarp{explore_dim_1}{.5}{Motion for varying just dimension 1}{}

\figvarp{explore_dim_2}{.5}{Motion for varying just dimension 2}{}

\figvarp{explore_dim_3}{.5}{Motion for varying just dimension 3}{}

\figvarp{explore_dim_4}{.5}{Motion for varying just dimension 4}{}

\figvarp{explore_dim_5}{.5}{Motion for varying just dimension 5}{}
